Proposed Solution

### 2016-11-11 Ennan-Proposal/solutions.tex
details in learner

\begin{figure}[!h]
\begin{small}
\belowdisplayskip=-15pt
\abovedisplayskip=-2pt
\begin{align*}
C :=&\ \text{Correct Learning Set}\\
C =&\ \text{\{Configuration Files in Intermediate Representation\}}\\
LR :=&\ \text{Learned Rules} :: \{\textrm{Rule}\}\\
LR =&\ \{ r\ \mid \forall file \in C,\ holds(r,file) \\
&\qquad \ \exists file \in C,\ nontriviallyHolds(r,file)\} 
\end{align*}
\end{small}
\caption{The definition of which rules should be learned by ConfigC}
\label{fig:configC}
\end{figure}

@@

@@

\begin{figure}[!h]
\begin{small}
\belowdisplayskip=-15pt
\abovedisplayskip=-2pt
\begin{align*}
U\ :=&\ \text{Unlabeled Learning Set}\\
U =&\ \text{\{Configuration Files in Intermediate Representation\}}\\
LP :=&\ \text{Learned Probabilistic Rules :: \{P\_Rule\}}\\
LR =&\ \{ r\ \mid \Pi file \in C,\ holds(r,file)\ \land \\
&\qquad  \ \Psi file \in C,\ nontriviallyHolds(r,file)\} 
\end{align*}
\end{small}
\caption{The definition of which rules should be learned by ConfigV when learning over a set of possibly correct, and possibly incorrect files.}
\label{fig:configV}
\end{figure}

We use $\Pi$ and $\Psi$ in Fig~\ref{fig:configV} to indicate that the rule holds for some critical portion of the files.
The inuition behind these quantifiers are that we want to consider rules which are true in majority of cases ($\Pi$), 
and for which we have at least some examples for which that rule is nontrivially true ($\Psi$).
The exact definition of $\Pi$ and $\Psi$ is a research question still to be solved.
What exactly is the cutoff value that will yield the best results in learning.
We plan to try multiple strategies to find these values.
One approach may be to use machine learning for program optimization, with a tool like OpenTuner~\cite{ansel:pact:2014}.
It is also possible that this value differs depending on the quality of the learning set and/or the particular type of rule being learned.

>>>>

\begin{figure}[!h]
\begin{small}
\belowdisplayskip=-15pt
\abovedisplayskip=-2pt
\begin{align*}
C ::&\ \text{Correct Learning Set}\\
C =&\ \text{\{Configuration Files in Intermediate Representation\}}\\
LR ::&\ \text{Learned Rules} :: \{\textrm{Rule}\}\\
LR =&\ \{ r\ \mid \forall file \in C,\ holds(r,file) \\
&\qquad \ \exists file \in C,\ nontriviallyHolds(r,file)\} 
\end{align*}
\end{small}
\caption{The definition of which rules should be learned by ConfigC}
\label{fig:configC}
\end{figure}

@@

We chose to employ this approach in our earlier work~\cite{santolucitoCAV} because any rule produced is guaranteed to be a correct rule.
As opposed to a traditional machine learning approach, we have here a formal guarantee of rule coverage.
Furthermore, by design this approach gives a justification (error location) for the classification of a user file as correct or misconfiguration.
This approach is most closely related to version space learning~\cite{mitchell77}, which we discuss further in Sec.~\ref{sec:travis}.

@@

\begin{figure}[!h]
\begin{small}
\belowdisplayskip=-15pt
\abovedisplayskip=-2pt
\begin{align*}
U ::&\ \text{Unlabeled Learning Set}\\
U =&\ \text{\{Configuration Files in Intermediate Representation\}}\\
LP ::&\ \text{Learned Probabilistic Rules :: \{P\_Rule\}}\\
LP =&\ \{ r\ \mid \Pi file \in C,\ holds(r,file)\ \land \\
&\qquad  \ \Psi file \in C,\ nontriviallyHolds(r,file)\} 
\end{align*}
\end{small}
\caption{The definition of which rules should be learned by ConfigV when learning over a set of possibly correct, and possibly incorrect files.}
\label{fig:configV}
\end{figure}

We use $\Pi$ and $\Psi$ in Fig~\ref{fig:configV} to indicate that the rule holds for some critical portion of the files.
The intuition behind these quantifiers are that we want to consider rules which are true in majority of cases ($\Pi$), 
and for which we have at least some examples for which that rule is nontrivially true ($\Psi$).
The exact definition and implementation of $\Pi$ and $\Psi$ is a research question still to be solved.
Even taking a simple majority voting approach, we must find the cutoff value that will yield the best results in learning.
We plan to try multiple strategies to find these values.
One approach may be to use machine learning for program autotuning, with a tool like OpenTuner~\cite{ansel:pact:2014}.
This requires creating some cost function for which the autotuning can optimize.
Additionally, it is possible that $\Pi$ and $\Psi$ differ depending on the quality of the learning set and/or the particular type of rule being learned.
Building a clear formalization and a modular tool to explore these questions is major task.

Note that this approach differs from a unsupervised learning setting~\cite{hastie2009unsupervised} where the training set is completely unlabelled and seeks to discover some hidden underlying strucutre.
Although still unlabelled, we make the assumption that some majority of the training set must be correct.
We are again learning a model which will provide clear justification (error locations) for the classification.
However, now we do not have the formal guarantees of the ConfigC approach.
From previous work, we believe this is a worthwhile trade-off in order to decrease the fasle positive rate.

### 2016-11-11 Ennan-Proposal/travis.tex
details in learner

One such example of such a training set of configuration files is TravisCI~\cite{travis}.
TravisCI, a popular integration and build testing service connected to Github.
TravisCI allows programmers to automatically run their test suite on a fresh virtual machine every time they commit their code.
A TravisCI user must add a configuration file to the repository that specifies build conditions, 
such as which dependencies are required, and a set of benchmarks to test. 
The results of these tests (indicating either passing, failing, or misconfiguration) 
are saved by TravisCI on a publicly available database~\cite{API}.

@@

Version space learning builds a logical constraint model for binary
classification~\cite{mitchell82}, which we use to test a configuration file for membership
in the set of all correct files~.
Traditional version space learning builds a model that tests membership
using a series of disjunctions from a set of predefined hypotheses.
Here we will instead use a conjuctions to convey that a configuration file must meet the learned criteria.
This extension will build a logical formula representing the entire 
history of examples, and use an SMT solver to find a classification model.

>>>>

One such example of such a training set of configuration files is TravisCI~\cite{API}.
TravisCI, a popular integration and build testing service connected to Github.
TravisCI allows programmers to automatically run their test suite on a fresh virtual machine every time they commit their code.
A TravisCI user must add a configuration file to the repository that specifies build conditions, 
such as which dependencies are required, and a set of benchmarks to test. 
The results of these tests (indicating either passing, failing, or misconfiguration) 
are saved by TravisCI on a publicly available database~\cite{API}.

@@

Version space learning builds a logical constraint model for binary
classification~\cite{mitchell77}, which we use to test a configuration file for membership
in the set of all correct files~.
Traditional version space learning builds a model that tests membership
using a series of disjunctions from a set of predefined hypotheses.
Here we will instead use a conjuctions to convey that a configuration file must meet the learned criteria.
This extension will build a logical formula representing the entire 
history of examples, and use an SMT solver to find a classification model.
